NIRCam Flux Calibration Plan

### 2017-02-14 ms.tex
I added some notes about NIRSpec, MIRI and possible problesm with white dwarfs after a discussion with George.

>>>>

\subsection{Sections to Expand in this Report}

George has some requests for this report.
Consider adding notes on calibration of two more instruments.
The solar spectrum is very well measured at infrared wavelengths, so it may be the best one for interpolation from optical/NIR into Far IR.
\begin{enumerate}
	\item MIRI: For the shorter wavelength MIRI bands (say F560W and F770W) photometry, George would like to observe the NIRCam faint G2V stars in order to have a sample of stars that have a highly accurate solar model
	\item NIRSpec: We'd also want to test calibration of NIRSpec w/ our solar G2 V stars.
George recommends the IFU or slits as opposed to MSA because it's less sensitive to positional accuracy.
Note that we would only get 1 G2V star at a time.
Also, beware that no bright stars from the cluster contaminate the field. MSA shutters that are stuck open may introduce significant amounts of stray light.
\end{enumerate}
Note, that George has two concerns about white dwarfs:
\begin{enumerate}
	\item debris disks emission - they have found that magnetic field trapping of dust around A stars can cause excess emission.
White dwarfs have strong magnetic fields and could also trap nano-grain dust.
George and Andras will probably write a paper on white dwarf dust in Fall of 2017.
	\item uncertainties in the IR - white dwarfs don't have a lot of measurements in the IR.
How can we be sure the models are good in the infrared?
\end{enumerate}
